---
title: "Data"
# subtitle: "Energy Statistics"
---

```{r}
#| label: setup
#| include: false

source("../src/utils_quarto.R")
```




# Level 3 Data
### PCE
Level 3 data applies statistical outlier checks in order to screen values for statistical anomalies. [Mean Absolute Deviation (MAD)](https://en.wikipedia.org/wiki/Median_absolute_deviation) was calculated for the following columns, then strong and extreme outliers were flagged/removed from the data.

```{r}
#| echo: false
#| results: asis
#|
render_outlier_rules(
  yaml_path  = "../config/check_data/l3_pce_outlier_check.yml",
  config_key = NULL
)

```

#### Downloads

```{r}
#| echo: false
#| results: asis

generate_download_table(
  data_dir       = "data/l3_outliers_checked/consolidated",
  file_pattern   = "\\.csv$"
)
```


<br>
<br>

# Level 2 Data
Level 2 data processing applies basic transformations to create or modify columns.

### PCE

```{r}
#| echo: false
#| results: asis

generate_download_table(
  data_dir       = "data/l2_transformed/consolidated",
  file_pattern   = "\\.csv$"
)
```


<br>
<br>

# Level 1 Data
Level 1 data is created by running basic data quality checks against the data and overwriting with NULL for values outside the boundaries. For instance, the column `most_recent_fuel_purch_price` requires values to be greater than $0.50 and less than $10.00. If a record contains a value of $0.20 or $50.00, the value is discarded. A list of records with out-of-bound values can be seen on [Quality and Outliers](quality_and_outliers.qmd)

### PCE

```{r}
#| echo: false
#| results: asis

render_quality_rules(
  yaml_path  = "../config/check_data/l1_pce_quality_check.yml",
  config_key = "l0_pce_header"
)
```

#### Downloads

```{r}
#| echo: false
#| results: asis

generate_download_table(
  data_dir       = "data/l1_quality_checked/consolidated",
  file_pattern   = "\\.csv$"
)

```

<br>
<br>

# Raw Data
### Monthly Power Cost Equalization (PCE)
Below are links to download archived copies of raw monthly data exported by the Alaska Energy Authority in XLSX format. These files are unprocessed and may contain errors. Use with caution.

```{r}
#| echo: false
#| results: asis

generate_download_table(
  data_dir       = "../data/raw",
  file_pattern   = "\\.xlsx$"
)
```
