---
title: "Quality and Outliers"
---

```{r}
#| label: setup
#| include: false

source("../src/utils_quarto.R")
```

In order to provide the most accurate version of this essential data, we performed two levels of checks. First, we set up and enforced basic boundary rules to ensure the data was within reasonable bounds. Second, we set up and ran statistical analysis in order to drop extreme anamolies within the data. For transparency, logs of the the removed records are shown below.




# Quality
Quality checks were performed on raw data in order to enforce boundaries.


```{r}
#| echo: false
#| results: asis

generate_download_table(
  data_dir       = "../data/l1_quality_checked/logs",
  github_subpath = "data/l1_quality_checked/logs",
  file_pattern   = "\\.csv$"
)

```


<br>
<br>


# Outliers
Outlier detection was performed on Level 2 data in order to identify and NULL extreme values.
```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(DT)

outliers <- read_csv("../data/l3_outliers_checked/logs/l3_pce_outliers_log.csv")



datatable(
  outliers,
  extensions = 'Buttons',
  options = list(
    dom = 'Bfrtip',       # "B" defines where buttons go, "f" is filter, "t" is table, "p" is pagination
    buttons = list(
      list(
        extend = 'csv',
        filename = 'outliers',
        text = 'Download CSV'
      ),
      list(
        extend = 'excel',
        filename = 'outliers',
        text = 'Download Excel'
      )
    ),
    pageLength = 15,       # Show 10 rows at a time
    scrollX = TRUE         # Makes wide tables scrollable horizontally
  ),
  rownames = FALSE,
  class = 'cell-border stripe hover'
)

```
